### 2016-10-31 methodsPaper/tex/introduction.tex
publically -> publicly

Here we present this implementation using publically-available datasets with coverage of the entire United States, and investigate the sensitivity of the model outputs to variability in the input parameters. The results of this work suggest that statistical modeling and tools like the custom-built \R{} package \package{} can improve the application of this useful methodology and increase its utility to both practicioners and researchers.

>>>>

Here we present this implementation using publicly-available
datasets with coverage of the entire United States, and investigate
the sensitivity of the model outputs to variability in the input
parameters. The results of this work suggest that statistical modeling
and tools like the custom-built \R{} package \package{} can improve
the application of this useful methodology and increase its utility to
both practicioners and researchers.
